Introducing Distributed Dynamic Data-intensive (D3) Science: Understanding Applications and Infrastructure

### 2016-08-18 3dpas_intro.tex
minor changes to Neil's addition

The landscape of scientific and enterprise computing is being fundamentally
altered by prodigious volumes of data.  
%Occasionally data are often naturally
%distributed and have to be processed near their source, and sometimes data that
%are localized have to be distributed in order to be processed, Data can be naturally distributed because they are
%being created in a set of distributed locations, rather than in one place. 
Data can also be transported to be processed in multiple, distributed
locations, rather than being processed near their source, or be brought together for processing at
a particular location. These two orthogonal dimensions lead to a number of patterns of data
generation and processing being present in real applications,
either for reasons of performance or for collaborative analytics.  
Further, the variation of data production rates, data source and destination makes 
temporal variations in data properties increasingly important.  
With an increase in the importance of distributed and temporal properties of 
data, systems and infrastructure aspects such as resource scheduling, d
ata placement, and transfer decisions that
were statically determinable at small scales emerge as dynamic and important
considerations at large scales of data and distribution.

>>>>

The landscape of scientific and enterprise computing is being fundamentally
altered by prodigious volumes of data.  
%Occasionally data are often naturally
%distributed and have to be processed near their source, and sometimes data that
%are localized have to be distributed in order to be processed, Data can be naturally distributed because they are
%being created in a set of distributed locations, rather than in one place. 
Data can also be transported to be processed in multiple, distributed
locations, rather than being processed near their source, or be brought together for processing at
a particular location. These two orthogonal dimensions lead to a number of patterns of data
generation and processing being present in real applications,
either for reasons of performance or for collaborative analytics.  
Further, the variation of data production rates, data source, and destination makes 
temporal variations in data properties increasingly important.  
With an increase in the importance of distributed and temporal properties of 
data, systems and infrastructure aspects such as resource scheduling, 
data placement, and transfer decisions that
were statically determinable at small scales emerge as dynamic and important
considerations at large scales of data and distribution.
